Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-01-31 paper/paper.tex
Update to SOSYM style and add summary new content to add

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}

@@

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
\and
\IEEEauthorblockN{
Konrad Slind, Isaac Amundson, Darren Cofer}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Minneapolis, Minnesota}
\and
\IEEEauthorblockN{
Junaid Babar, David Hardin}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Cedar Rapids, Iowa}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\IEEEpeerreviewmaketitle

\section{Introduction} \label{sec:intro}
\input{intro}

\section{Simple Example} \label{sec:example}
\input{example}

@@

%\section*{Acknowledgments}
%This work was sponsored in part by the Defense Advanced Research
%Projects Agency (DARPA).

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section
\clearpage
\bibliographystyle{IEEEtran}
\bibliography{paper}

>>>>

% TODO: add in the referee tag for the submission
%\documentclass[global,twocolumn,referee]{svjour}
\documentclass[global,twocolumn]{svjour}
\usepackage{cite}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}

@@

% \theoremstyle{plain}
% \newtheorem{theorem}{Theorem}
% \newtheorem{lemma}{Lemma}

% \theoremstyle{definition}
% \newtheorem{definition}{Definition}

% \theoremstyle{remark}
% \newtheorem{remark}{Remark}

\journalname{Software and Systems Modeling}

@@

\author{
  Eric Mercer\inst{1}    \and 
  Konrad Slind\inst{2}   \and
  Isaac Amundson\inst{2} \and
  Darren Cofer\inst{2}   \and
  Junaid Babar\inst{3}   \and
  David Hardin\inst{3}
}

\institute{
  Brigham Young University        \\
  Provo, Utah                     \and
  Applied Research and Technology \\ 
  Collins Aerospace               \\
  Minneapolis, Minnesota          \and
  Applied Research and Technology \\ 
  Collins Aerospace               \\
  Cedar Rapids, Iowa
}

\date{Received: date / Revised version: date}

@@

\section{Introduction} \label{sec:intro}
\input{intro}
\subsection{SOSYM Journal Details}
The submission must have 30\% new material over what was published in MODELS 2021.
There is no page limit.
The article will go through a full review cycle.
The due date is \textbf{March} $1^\mathrm{st}$, \textbf{2022}.

\noindent The summary of the discussion regarding how the MODELS publication might be extended is given below.
\begin{compactitem}
  \item Expand the case study with the TA6 models
  \item Expand the case study with an actual full AGREE specification
  \item AGREE formal semantics summary including the uninterpreted functions
  \item Strengthen the assurance argument from AGREE to binary by way of CakeML
  \item Expand related work (add recent work published after 2018). 
  \item Respond more fully to the reviews from MODELS (see below).
\end{compactitem}

\noindent The summary of items from the MODELS reviews.
\begin{compactitem}
  \item Add recent work published after 2018
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
  \item Expand the role of Briefcase in the case study with input examples to provide more proof of the proposed model's effectiveness on the hardened system (e.g., show a malformed line search task, it's filter, and why it works) 
  \item Clarify research questions answered by the case study and make the figures bigger
  \item Discuss what efforts are optimized with the automations versus a fully manual process for creating the components--how does the automated transformation affect actual time for engineers
  \item Without verifying the correctness of the transformations, can prevention of certain attacks be guaranteed?
\end{compactitem}
\section{Simple Example} \label{sec:example}
\input{example}

@@

\clearpage
\bibliographystyle{plain}
\bibliography{paper}
